---
title: "Friends"
description: |
  A short description of the post.
author:
  - name: Andrew Stewart
    url: https://www.andrewcstewart.com
date: 09-08-2020
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Packages
library(tidytuesdayR)
library(tidyverse)
library(janitor)
library(here)
library(ggplot2)
library(patchwork)
library(waffle)

theme_set(theme_minimal())

# First update the tidyduesdayR master file
tidytuesdayR:::tt_update_master_file(force=TRUE)

tt <- tt_load("2020-09-08")

print(rmarkdown::metadata$date)
```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}
# main_friends <- tt$friends %>% 
#   tabyl(speaker) %>% 
#   arrange(desc(n)) %>% 
#   head(6) %>% 
#   pull(speaker)
# 
# # df <- tt
# df <- tt$friends %>%
#   count(season, speaker) %>%
#   filter(speaker %in% main_friends)
```

# Visualize

Using your processed dataset, create your unique visualization.

```{r fig.height=8, fig.width=6}
main_friends <- tt$friends %>% 
  tabyl(speaker) %>% 
  arrange(desc(n)) %>% 
  head(6) %>% 
  pull(speaker)

# df <- tt
df <- tt$friends %>%
  count(season, speaker) %>%
  mutate(n = n/10) %>%
  filter(speaker %in% main_friends)

p1 <- ggplot(df, aes(fill = speaker, values = n)) +
  geom_waffle(color = "white", size = .25, n_rows = 5, flip = TRUE) +
  facet_wrap(~season, nrow = 1, strip.position = "bottom") +
  scale_x_discrete() + 
  scale_y_continuous(labels = function(x) x * 10, # make this multiplyer the same as n_rows
                     expand = c(0,0)) +
  ggthemes::scale_fill_tableau(name=NULL) +
  coord_equal() +
  labs(
    # title = "TidyTuesday: Friends",
    # subtitle = "Number of lines ",
    x = "Season",
    y = "Count (each square = 10 lines)"
  ) +
  theme_minimal(base_family = "Roboto Condensed" ) +
  theme(panel.grid = element_blank(), axis.ticks.y = element_line()) +
  # theme_ft_rc() +
  guides(fill = guide_legend(reverse = TRUE))

p1 + plot_annotation(
  title = "Friends!",
  subtitle = "Who had the most lines?",
  caption = "Created by @andrewcstewart, Data from the {friends} package, #TidyTuesday",
  # theme = theme_ft_rc()
  ) 
```



Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.


